\Title

### 2021-06-04 latex/paper/main.tex
Forgot about showing the origin is a repeller / stable, started doing that now.

\subsection{Energy gain on \(\mathcal{O}_1\)}
We will now prove the first part of Theorem
\ref{thm:acrobot-energy-stabilization}.
We choose \(D\) in Lemma \ref{lemma:energy-regulation-D} to be the
annulus \(\mathcal{O}_1 \backslash \{(0,0)\}\) consisting of all oscillations of
the nominal pendulum.
Using the procedure described by Mohammadi \etal 
\cite{dynamic_vhcs_stabilize_closed_orbits} for finding pseudo-polar
coordinates adapted to level sets of \(E\), we compute
\begin{align}
    \label{eqn:r-osc}
    r &= \arccos\left(\cos(q_u) - \frac{p_u^2}{30m^2gl^3}\right)
    , \\
    \label{eqn:theta-osc}
    \theta &=
    \left.\arctan_2\left(-\sign{p_u}\sqrt{1-\frac{q_u^2}{r^2}},\frac{q_u}{r}\right)
    \right|_{r = r(q_u,p_u)}
    ,
\end{align}
where \(r \in \, ]0,\pi[\).
This has inverse
\begin{align*}
    q_u &= r\cos(\theta)
    , \\
    p_u &= -\sign{\sin(\theta)}
    \sqrt{30m^2gl^3(\cos(rc_\theta - c_r)}
    .
\end{align*}
We now verify these coordinates satisfy the requirements of 
Lemma \ref{lemma:energy-regulation-D}.

@@

Next we compute
\(b(\theta,r_0) = (\partial g/\partial I)(\theta, r_0, 0) = K a(\theta,r_0)\),
where
\begin{align*}
    K &:= \frac{\bar{q}_a \sqrt{30m^2g l^3}}{15}
    , \\
    a(\theta,r_0) &:= \frac{
        r_0 |\sin(\theta)| \left(
        5 c_{r_0} \cos(r_0 c_\theta) - 8 \cos(r_0c_\theta)^2 + 3
    \right)
    }{
    \sin(r_0)\sqrt{\cos(r_0c_\theta) - c_{r_0}}
    }
    .
\end{align*}
Notice that \(K\) is a positive constant which depends only on
\(m\),\(g\),\(l\), and \(\bar{q}_a\).
This means that there exists \(\epsilon > 0\) such that 
\(S(r_0) := \int_0^{2\pi} b(\sigma,r_0)d\sigma \geq \epsilon\)
if and only if \(Q(r_0) := \int_0^{2\pi} a(\sigma,r_0) d\sigma\) is strictly
positive for all \(r_0 \in \, ]0,\pi[\).
Since \(a(\theta,r_0)\) is adimensional, we can numerically compute \(Q(r_0)\)
once for all acrobots.
The plot of \(Q(r_0)\) when \(r_0 \in [10^{-10}, \pi - 10^{-3}]\) is shown in
Figure \ref{fig:acrobot-Q}.
We see that it is strictly positive and monotonically increasing, with an
asymptote at \(r_0 = \pi\).
Simulations with smaller \(r_0\) result in an infinite integral error due to a
division by zero, yet we believe the \(Q(r_0)\) is in fact positive for all 
\(r_0 \in \, ]0,\pi[\).

\begin{figure}
    \centering
    % TODO: Show this plot
    %\includegraphics[width=0.8\linewidth]{}
    \caption{The plot of \(Q(r_0)\).}
    \label{fig:acrobot-Q}
\end{figure}

Finally, \(a(\theta,r_0)\) is clearly \(2\pi\)-periodic in \(\theta\),
which means all conditions of Lemma \ref{lemma:energy-regulation-D}
are satisfied. 
Therefore, the acrobot is gaining energy everywhere on
\(D = \mathcal{O}_1 \backslash \{(0,0)\}\).
The origin must be a repeller (otherwise Lemma
\ref{lemma:energy-regulation-D} would fail), so we conclude that the acrobot
is gaining energy on \(\mathcal{O}_1\).

>>>>

\subsection{Energy gain on \(\mathcal{O}_1\)}
We will now prove the first part of Theorem
\ref{thm:acrobot-energy-stabilization}.
We begin by studying the punctured open set
\(\mathcal{O}_1 \backslash \{(0,0)\}\) consisting of all (nonzero) oscillations
of the nominal pendulum.
Using the procedure described by Mohammadi \etal 
\cite{dynamic_vhcs_stabilize_closed_orbits} for finding pseudo-polar
coordinates adapted to level sets of \(E\), we compute
\begin{align}
    \label{eqn:r-osc}
    r &= \arccos\left(\cos(q_u) - \frac{p_u^2}{30m^2gl^3}\right)
    , \\
    \label{eqn:theta-osc}
    \theta &=
    \left.\arctan_2\left(-\sign{p_u}\sqrt{1-\frac{q_u^2}{r^2}},\frac{q_u}{r}\right)
    \right|_{r = r(q_u,p_u)}
    ,
\end{align}
where \(r \in \, ]0,\pi[\).
This has inverse
\begin{align*}
    q_u &= r\cos(\theta)
    , \\
    p_u &= -\sign{\sin(\theta)}
    \sqrt{30m^2gl^3(\cos(rc_\theta - c_r)}
    .
\end{align*}
We now verify these coordinates satisfy the requirements of 
Lemma \ref{lemma:energy-regulation-D}.

@@

Next we compute
\(b(\theta,r_0) = (\partial g/\partial I)(\theta, r_0, 0) = K a(\theta,r_0)\),
where
\begin{align*}
    K &:= \frac{\bar{q}_a \sqrt{30m^2g l^3}}{15}
    , \\
    a(\theta,r_0) &:= \frac{
        r_0 |\sin(\theta)| \left(
        5 c_{r_0} \cos(r_0 c_\theta) - 8 \cos(r_0c_\theta)^2 + 3
    \right)
    }{
    \sin(r_0)\sqrt{\cos(r_0c_\theta) - c_{r_0}}
    }
    .
\end{align*}
Notice that \(K\) is a positive constant which depends only on
\(m\),\(g\),\(l\), and \(\bar{q}_a\), and \(a(\theta,r_0)\) is \(2\pi\)-periodic
in \(\theta\).
This means that there exists \(\epsilon > 0\) such that 
\(S(r_0) := \int_0^{2\pi} b(\sigma,r_0)d\sigma \geq \epsilon\)
if and only if \(Q(r_0) := \int_0^{2\pi} a(\sigma,r_0) d\sigma\) is strictly
positive for all \(r_0 \in \, ]0,\pi[\).
Since \(a(\theta,r_0)\) is adimensional, we can numerically compute \(Q(r_0)\)
once for all acrobots.
The plot of \(Q(r_0)\) when \(r_0 \in [10^{-10}, \pi - 10^{-3}]\) is shown in
Figure \ref{fig:acrobot-Q}.
We see that it is strictly positive and monotonically increasing, with an
asymptote at \(r_0 = \pi\).
Simulations with smaller \(r_0\) result in an infinite integral error due to a
division by zero, yet we believe the \(Q(r_0)\) is in fact positive for all 
\(r_0 \in \, ]0,\pi[\).
\begin{figure}
    \centering
    % TODO: Show this plot
    %\includegraphics[width=0.8\linewidth]{}
    \caption{The plot of \(Q(r_0)\).}
    \label{fig:acrobot-Q}
\end{figure}

While \(Q(r_0) \not \geq \epsilon\) on \(]0,\pi[\), it is certainly bounded
below on \(]\omega,\pi[\) for each fixed \(\omega > 0\).
This means all conditions of Lemma \ref{lemma:energy-regulation-D}
are satisfied on the set 
\[
    D_\omega = \mathcal{O}_1 \backslash 
    \{(q_u,p_u) \in \SxR \mid E(q_u,p_u) \leq E(\omega,0)\}
    .
\]
Therefore, for each \(\omega \in \, ]0,\pi[\) there exists some \(I_1^\star\)
such that the acrobot gains/loses energy everywhere on \(D_\omega\).
To prove energy gain on all of \(\mathcal{O}_1\), we will show the origin is a
repeller if \(I > 0\), and that it is an asymptotically stable equilibrium
if \(I < 0\).
Recall the Poincar\'{e} section used in the proof of Lemama
\ref{lemma:energy-regulation-D}.
\textbf{TODO: Show the origin is a repeller/stable eqm via the poincare map}.
